\LARGE \bf Matrix Multiplication-Driven Repulsive Fields for 3D Voxel-Based TSDF Calculation

### 2024-03-17 Articles/IROS/root.tex
edited translational velocity

@@

\begin{equation}
	\dot{q} = J^+ \xi_{p} \mathrm{\vec{v}_{att}} + \dot{q}_{rep}
\end{equation}

The damped Moore-Penrose pseudo-inverse, \(J^+~=~J'(JJ' + \sigma_{ee} I)^{-1}\), is utilized to mitigate singularity issues and improve numerical stability in inverse kinematics computations. $\xi_{p}$ is the primary task execution slowdown constant. Finally $\dot{q}_{REP}$ are the weighted sum of avoidance joint velocities, each transformed into the null space of primary velocities, as described in the chapter below. \remove{For redundant robots, it optimizes solution selection by minimizing the joint velocity norm, while damping is applied to limit excessive joint velocities near singular configurations, thus improving solution robustness.}

\add{maybe add the middle joints component in the equation (it is not necessary, doesn't make much change in the chosen experiments)}

@@

Vodenje vrha manipulatorja (end-effector) je naloga z najvišjo prioriteto.

\remove{Our method employs inverse kinematics approach (IK) to guide the end effector (EE) towards its target, marking a departure from Khatib's joint coordinates approach in favor of a Cartesian coordinates framework. This is particularly beneficial in scenarios involving redundant manipulators, where determining an optimal goal joint configuration in advance is challenging.}

When calculating translational velocity, we avoid the conventional gradient of the squared distance approach, which leads to high initial velocities and subsequently slow speeds near the target. Our aim is a consistent velocity throughout the trajectory, with controlled deceleration near the goal. This is achieved by first calculating the unit vector towards the target for direction, then modulating its magnitude using a sigmoid function, specifically the arctangent function, to prevent overshooting and ensure stable approaching motion.

@@

In the above equation (eq.~\ref{eq: v_att}), $\vec{v}$  represents the end effector's translational velocity towards the target, combining direction and magnitude. The terms $\vec{x}_{EE}$ and $\vec{x}_g$ denote the current and goal positions of the EE, respectively, in Cartesian coordinates. The unit vector calculation, $\frac{\vec{x}_{EE}-\vec{x}_g}{||\vec{x}_{EE}-\vec{x}_g||}$, ensures motion directed towards the target. Finally, the sigmoid function, particularly the arctangent component, modulates this velocity to avoid overshooting, balancing speed and precision. The constant $k_{sigm}$ allows us to set how close to the goal does the robot EE start slowing down.

@@

@@

>>>>

\alert{equations break column}

@@

%\begin{equation}
%	\dot{\vec{q}} = J^+ \xi_{p} \mathrm{\vec{v}_{att}} + \dot{\vec{q}}_{rep}
%\end{equation}

\begin{equation}
	\dot{\vec{q}} = \mathbf{J}^+ \xi_{p} \mathrm{\vec{v}{att}} + \dot{\vec{q}}_{rep}
\end{equation}

The damped Moore-Penrose pseudo-inverse, \(\mathbf{J}^+~=~\mathbf{J}'(\mathbf{J}\mathbf{J}' + \sigma_{ee} \mathbf{I})^{-1}\), is utilized to mitigate singularity issues and improve numerical stability in inverse kinematics computations. $\xi_{p}$ is the primary task execution slowdown constant. Finally $\dot{\vec{q}}_{rep}$ are the weighted sum of avoidance joint velocities, each transformed into the null space of primary velocities, as described in the chapter below.

%\remove{For redundant robots, it optimizes solution selection by minimizing the joint velocity norm, while damping is applied to limit excessive joint velocities near singular configurations, thus improving solution robustness.}

%\add{maybe add the middle joints component in the equation (it is not necessary, doesn't make much change in the chosen experiments)}

@@

%Vodenje vrha manipulatorja (end-effector) je naloga z najvišjo prioriteto.

Prioritizing control over the end-effector's (EE) translational velocity is essential for a consistent and stable target approach. The commonly used method, where translational velocity is proportional to squared distance, leads to impractically high initial velocities, which can prevent obstacle avoidance and real-world execution, followed by disproportionately slow velocities when nearing the goal position. Our aim is a consistent velocity profile throughout the trajectory, with controlled deceleration near the goal. This is achieved by first calculating the unit vector towards the target for direction, then modulating its magnitude using a sigmoid function, specifically the arctangent function (Eq. \ref{eq: v_att}).

@@

%In the above equation (eq.~\ref{eq: v_att}), $\vec{v}$  represents the end effector's translational velocity towards the target, combining direction and magnitude. The terms $\vec{x}_{EE}$ and $\vec{x}_g$ denote the current and goal positions of the EE, respectively, in Cartesian coordinates. The unit vector calculation, $\frac{\vec{x}_{EE}-\vec{x}_g}{||\vec{x}_{EE}-\vec{x}_g||}$, ensures motion directed towards the target. Finally, the sigmoid function, particularly the arctangent component, modulates this velocity to avoid overshooting, balancing speed and precision. The EE velocity will be transformed using the sigmoid curve when near the goal. When the distance from goal point is high, the sigmoid will cause the velocity to get into saturation, that is upper limit. The constant $k_{sigm}$ allows us to set how close to the goal does the robot EE start slowing down and what is the velocity profile when approaching the goal point.

In Eq.~\ref{eq: v_att}, $\vec{v}$ specifies the end-effector's (EE) translational velocity directed towards the target, integrating both its direction and magnitude. Here, $\vec{x}_{EE}$ represents the EE's current position, and $\vec{x}g$ is the target position, both in Cartesian coordinates. The calculation $\frac{\vec{x}{EE}-\vec{x}g}{||\vec{x}{EE}-\vec{x}g||}$ generates a unit vector pointing towards the target, ensuring targeted movement. The velocity's modulation by the arctangent sigmoid function curtails overshooting by moderating speed in proximity to the target and saturating velocity at a predefined upper limit when distant. The parameter \(k_{sigm}\) in the arctangent function adjusts the curve's steepness, affecting how quickly the end-effector decelerates near the target. A higher \(k_{sigm}\) maintains speed until closer to the target for a sharp deceleration, while a lower value starts slowing down earlier for a gradual approach.

@@

\alert{add the limits of joint positions}

@@

\add{sigmoid weights}
